---
title: "Phase3_Modelling"
author: "Chaytanya Kumar & Pape Theodore"
date: "4/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(broom)
library(GGally)
library(onewaytests)
library(lbutils)
```



```{r}
DataSet_final <- read_csv("~/Documents/STAT_615_Regression/Regression_ Project/DataSet_final.csv")
view(DataSet_final)
```
```{r}
DataSet_final <- read.csv("~/Documents/STAT_615_Regression/Regression_ Project/DataSet_final.csv",header = T,na.strings = c("","NA"))
class(DataSet_final$email)
summary(DataSet_final)   #NA's replaced with Zero 
dim(DataSet_final)
```




```{r}
DataSet_final$Active3M <- as.factor(DataSet_final$Active3M)
DataSet_final$response <- as.factor(DataSet_final$response) #ordinal values

```

```{r}
library(caret)   #use for partitioning
set.seed(1240) 
index <- createDataPartition(DataSet_final$response,p=0.8,list=F)  #not list #randonly selected and not biased 
index

# 80% training and 20% test data

#View(index)
Master_Train <- DataSet_final[index,]  #rows and then columns
Master_Train



#dim(Master_Train)  #80 percent , 982: Observations 21: Variables

Master_Test<- DataSet_final[-index,]
dim(Master_Test)   # 20 percent , 245:Observations 21: variables 

```







```{r}
Full <- glm(response~email+sms+call+n_comp+loyalty+portal+rewards+nps+n_yrs+
                 Region+Sales2019+B1Sales2019+B1Contribution+Active3M+
                 BuyingFrequency2019+B1BuyingFrequency+BrandEngagement,data=Master_Train,family=binomial)
summary(Full)
```

```{r}
#Stepwise Forward Method to align the Variables 

NUll_Model <- glm(response~1,Master_Train,family = binomial) #there is no predictor 

Fullstep<-step(NUll_Model,scope=list(lower=NUll_Model,upper=Full),direction="forward")
summary(Fullstep)
```


#email : more the number of email more are the chances to respond 
#sms : if we sent more sms then the probability of responding will be increased 
#call :  more the number of calls more are the chances to respond
#loyalty : If the ChannelPartner is loyal, he is likely to respond
#rewards : if the reward is redeemed then the it more likely that they will not respond 
#nps : net promoter score : more the score the probability of responding will be increased 
#Sales2019 : more amount of Sales more likely to respond 
##
#Model Equation : y = bo+ b1(email) + b2(sms) + b3(calls) +b4(loyalty) +b5(rewards)+
#                         b6(nps) + b7(n_yrs) +b8(Sales2019)

#Model Equation  : 3.115e+00 + 1.397e+00(email)+ 3.623e-01(sms) + 2.351e+00(calls) + 3.589e+00(loyalty) +
#                              (-5.480e+00 )(rewards) + 1.558e-01(nps)+
#                       8.141e-02 (n_yrs) + (5.171e-06 )(Sales2019)




```{r}
#Checking for Multi-colinearity of the variables 

library(car)
vif(Fullstep)

#There is no severe multicollinearity so we will keep all the viarables. 

############## Main model############
#With Reward 
Fullstep<-glm(formula = response ~ email + rewards + loyalty + call + nps + 
    B1Sales2019 + n_yrs + sms + Sales2019, family = binomial, 
    data = Master_Train)

summary(Fullstep)



```



```{r}
#Global Hypothesis Testing 

#H0 = All the variables insignificant
#H1 = Atleast one of the variable is significant 

NUll_Model <- glm(response~1,data=Master_Train,family = binomial)
anova(Fullstep,NUll_Model,test="Chisq") 



#P-value < 0.05 Reject Ho : Hence it proves that at least one of the variable is significant.

```



```{r}
#Calculate Area under the curve , ROCR for traindata 


#We also compared it without reward and found  that ROC was 72%.
#With reward 84%

library(ROCR)
Predprob_Response <- round(fitted(Fullstep),2)
head(Predprob_Response)

Prediction_Response <- prediction(Predprob_Response,Master_Train$response)
Performance_Response <- performance(Prediction_Response,"tpr","fpr")
plot(Performance_Response)
abline(0,1)


Auc_Response <- performance(Prediction_Response,"auc")
Auc_Response@y.values  # [1] 0.84 = 84.27%


```



```{r}
#Validating the Model on the Test Data on Test data 

Predprob_Test <- round(predict(Fullstep,Master_Test,type='response'),2)
head(Predprob_Test)

Prediction_Test <- prediction(Predprob_Test,Master_Test$response)
Performance_Test <- performance(Prediction_Test,"tpr","fpr")
plot(Performance_Test)
abline(0,1)

Auc_Test <- performance(Prediction_Test,"auc")
Auc_Test@y.values    #[1] 0.84 = 84.97%


```

